\documentclass[11pt]{article}

\usepackage{xcolor}
\usepackage{tabularx}

% Page layout
\usepackage{geometry}
\newcommand\MARGIN{20mm}
\geometry{
    a4paper,
    left=\MARGIN,
    right=\MARGIN,
    top=\MARGIN,
    bottom=\MARGIN,
}

% Do not indent the first line of paragraphs
\setlength{\parindent}{0cm}

% Layout stuff
\usepackage{lastpage}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{Page \thepage \hspace{1pt} of \pageref{LastPage}}

% Custom section titles
\usepackage{titlesec}
\newcommand\TITLE[1]{\par{\centering{\Huge\textsc{#1}}\bigskip\par}}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{0.5cm}{0.3cm}

% URLs
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.15,0.4}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

% Bulletpoints instead of itemize, as they do not work well inside tables
\newcommand{\tabitem}{{\textbullet}~}

% Document structure
\begin{document}

\TITLE{Nicolas Forstner}

\begin{center}
\begin{tabular}{cc}
    \begin{tabular}{rl}
        \textsc{Mobile:} & +44 7379 400253 \\
        \textsc{Email:}  & \href{mailto:nls.forstner@gmail.com}{nls.forstner@gmail.com} \\
    \end{tabular} &
    \begin{tabular}{rl}
        \textsc{Homepage:} & \href{https:nforstner.com}{nforstner.com} \\
        \textsc{Based in:} & London \\
    \end{tabular}
\end{tabular}
\end{center}

\section{Education}

\begin{tabular}{r|l}
    % UNIVERSITY
    \textsc{2018-2022} &
        \begin{tabularx}{0.8\textwidth}{X}
            \textsc{University of York (Russel Group)} \\

            \emph{MEng (Hons) Computer Science with Artificial
            Intelligence} \\

            \tabitem Recipient of the IET Prize for the most outstanding student of my year. \\

            \tabitem First class honors with firsts in all four years of the
            degree. Transcript available on
            \href{https://nforstner.com/transcript.pdf}
            {nforstner.com/transcript.pdf}.

            \tabitem Third year thesis on object tracking using conventional
            video and optical flow. \\

        \end{tabularx} \\
    \multicolumn{2}{c}{} \\

    % SCHOOL
                  & \textsc{School} \\
    \textsc{2017} &
        \emph{German (Bavarian) \emph{Abitur} with a grade average of 1.6 (1 is
        best, 6 is worst)} \\

\end{tabular}

\section{Work Experience}

\begin{tabular}{r|l}

% UOY PROJECT

    \begin{tabular}{r}
        \textsc{June \&} \\
        \textsc{July} \\
        \textsc{2022} \\
    \end{tabular} &

    \begin{tabularx}{0.8\textwidth}{X}

        \textsc{University of York} \\

        \emph{Research support assistant - Telemedicine with AI for COVID-19
        patients} \\

        \tabitem Analysed and consolidated the team's research towards using AI
        to diagnose COVID-19 infections to prepare them for publication in
        journals such as \href{https://plos.org/}{PLOS}. \\

        \tabitem Developed integrations for AI models to facilitate their internal usage. \\

    \end{tabularx} \\

    \multicolumn{2}{c}{} \\

% ATOS 2

    \begin{tabular}{r}
        \textsc{July \&} \\
        \textsc{August} \\
        \textsc{2020} \\
    \end{tabular} &

    \begin{tabularx}{0.8\textwidth}{X}

        \textsc{Atos} \\

        \emph{Intern - Consulting for data science and artificial
        intelligence} \\

        \tabitem Contributed to a project for the German military (BWI)
        involving the detection of humans through walls using radio signals. \\

        \tabitem Trained a cross-modal teacher-student model and developed a
        complex data pipeline to process sensor data. \\

        \tabitem Presented the team’s work to customers and managed further
        communication as part of our SCRUM cycle. \\

    \end{tabularx} \\

    \multicolumn{2}{c}{} \\

% ATOS 1

    \begin{tabular}{r}
        \textsc{September} \\
        \textsc{2019}
    \end{tabular} &

    \begin{tabularx}{0.8\textwidth}{X}
        \textsc{Atos} \\

        \emph{Intern - Consulting for data science and artificial
        intelligence} \\

        \tabitem Developed software that uses machine learning to improve the
        efficiency of a production line for electrical parts in a Siemens
        factory. \\

        \tabitem By making heavy use of data preprocessing and hyper-parameter
        optimization, my approach was able to beat all alternatives and was
        chosen to be deployed into production. \\

    \end{tabularx} \\

    \multicolumn{2}{c}{} \\

% PADBERG

    \begin{tabular}{r}
      \textsc{August \&} \\
      \textsc{September} \\
      \textsc{2018}
    \end{tabular} &

    \begin{tabularx}{0.8\textwidth}{X}
        \textsc{Padberg \& Partners} \\

        \emph{Internship - Web development and task automation} \\

        \tabitem Contributed to the development of open-source marketing
        platform \textit{Mautics}. \\
        \tabitem Automated migrations from proprietary software to open-source
        alternatives. \\

    \end{tabularx}

\end{tabular}

\section{Skills}

\begin{tabularx}{\textwidth}{rX}
    \textsc{General} & Strong passion for deep learning with excellent
    engineering abilities. \\
    & Proven communication skills and exceptional ability

    to explain and teach. \\
    \textsc{AI} & Transformers, Denoising Diffusion,
                   Generative AI, implementation and debugging of
                   custom model architectures and training loops,
                   training on HPC clusters. \\
                 & PyTorch, Jax, DeepMind-Haiku, Hugging Face ecosystem, W\&B \\
    \textsc{Languages} & Python, Rust, JavaScript, LaTeX, some C and CUDA \\
    \textsc{Other} & Linux, Git, GitHub, Docker, Slurm, Google Cloud, AWS,
    NeoVim, web development with e.g. Flask and VueJs \\

    \multicolumn{2}{c}{} \\

    \textsc{English} & Excellent \\
    \textsc{German}  & Native \\

\end{tabularx}

\section{Selected Projects}

\begin{tabularx}{\textwidth}{rX}

    \textsc{MiniGPT} & A minimal re-implementation of OpenAI's GPT
    \textbf{language model} in Jax with DeepMind-Haiku. Features include:
    Telemetry logging to \href{https://wandb.ai}{W\&B}, multi-GPU training
    automatic mixed precision, gradient checkpointing, architectural
    improvements such as Rotary positional embeddings, pre-norm transformer
    blocks and SwiGLU activations.
    \href{https://github.com/nlsfnr/MiniGPT}{GitHub}. \\

    \multicolumn{2}{c}{} \\

    \textsc{Kigo} & A \textbf{diffusion model} to generate images. Features
    include (in addition to those above): DDIM sampling with impressive results
    after only 16 sampling steps, utilities for training on Slurm clusters,
    complete U-Net architecture implemented from scratch.
    \href{https://github.com/nlsfnr/Kigo}{GitHub}. \\

    \multicolumn{2}{c}{} \\

    \textsc{Timber} & A small \textbf{programming language}, consisting of a
    tokenizer, parser, code generator and a stack-based virtual machine. Includes
    functions, loops, conditionals, pointers and basic I/O. Check out this
    \href{https://github.com/nlsfnr/timber/blob/master/code.timber}{\textit{Hello
    World} program} written in Timber! \href{https://github.com/nlsfnr/timber}{GitHub}.
    \\

\end{tabularx}

\end{document}
